How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Sohon changes upto and including pag 3

\maketitle
\begin{abstract}
Block-based programming languages like Scratch, Alice and Blockly are becoming increasingly common as introductory languages in programming education. There is substantial research showing that these visual programming environments are suitable for teaching programming concepts. But, what do people do when they use Scratch? In this paper we explore the characteristics of Scratch programs. To that end we have scraped the Scratch public repository and retrieved 250.000 projects. We present an analysis of these projects in three different dimensions. Firstly, we look at the types of blocks used and the size of the projects. We then investigate complexity, used abstractions and programming concepts. Finally we detect \emph{code smells} like long scripts and duplicated code blocks. Our results show that 1) most Scratch program are small, however Scratch programs consisting of over 100 sprites exist, 2) programming abstraction concepts like procedures are not commonly used and 3) Scratch programs suffer do commonly from code smells including long methods and unmatched broadcast signals.
\end{abstract}

@@

We ran Kragle on March 2nd 2016 for 24 hours, when it had obtained a little over 250.000 projects. Out of the \nPrograms~, we failed to parse and further analyze 2.367 projects due to technical difficulties with the provided JSON files. Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/ScratchLover42/ICER-Data-Code}}

>>>>

\maketitle
\begin{abstract}
Block-based programming languages like Scratch, Alice and Blockly are becoming increasingly common as introductory languages in programming education. There is substantial research showing that these visual programming environments are suitable for teaching programming concepts. But, what do people do when they use Scratch? In this paper we explore the characteristics of Scratch programs. To that end we have scraped the Scratch public repository and retrieved 250,000 projects. We present an analysis of these projects in three different dimensions. Firstly, we look at the types of blocks used and the size of the projects. We then investigate complexity, used abstractions and programming concepts. Finally we detect \emph{code smells} like long scripts and duplicated code blocks. Our results show that 1) most Scratch program are small, however Scratch programs consisting of over 100 sprites exist, 2) programming abstraction concepts like procedures are not commonly used and 3) Scratch programs suffer do commonly from code smells including long methods and unmatched broadcast signals.
\end{abstract}

@@

We ran Kragle on March 2nd 2016 for 24 hours, when it had obtained a little over 250,000 projects. Out of the \nPrograms~, we failed to parse and further analyze 2,367 projects due to technical difficulties with the provided JSON files. Kragle, as well as all scraped projects and our analysis files are available.\footnote{\label{repo}\url{https://github.com/ScratchLover42/ICER-Data-Code}}
